### 2022-12-14 intro.Rnw
formatting and reproducibility

% How can we know if a finding from a scientific study is really true? For
% example, how can we know if the protective effect of a vaccine found in a study
% is real? The answer to such questions is of high importance to scientists,
% decision makers, and the general population. However, because any study result
% comes with uncertainty we can never know for sure.
How can we know whether we can trust a finding from a scientific study? For
example, how can we know whether the protective effect of a vaccine found in a
study is a genuine effect or just a spurious finding? The answer to such
questions is of high importance to researchers, decision makers, and the general
population, and one way to obtain it is through \emph{replication studies}.

A replication study consists of repeating the original study as close as
possible but with new subjects. Such a study may yield similar results which
would make us more confident about the original finding, or may yield
conflicting results which would lower our confidence. As such, replication
studies are an essential part of the scientific method as they provide a means
for substantiating genuine research findings and refuting research findings
which occurred merely by chance. For this reason, ``successful'' replication is
often a requirement, for instance, for acceptance of newly proposed scientific
theories (\eg{} a new physical model) or the implementation of policies based on
scientific knowledge (\eg{} market approval of a drug). The results from
replication studies may hence have real world consequences, % , such as deciding
% whether we receive the recommendation to get vaccinated (a consequence that
% anyone who experienced the COVID-19 pandemic is very aware of)
and it is therefore important that methodological aspects of replication
studies, such as their statistical design and analysis, are well understood.

@@

Most methods for analyzing replication studies can be formulated in terms of
study-level summary statistics as shown in Table~\ref{tab:meta}. % Effect
% estimates, standard error, confidence intervals, and $p$-values
All of these are routinely reported in research articles, and if one of them is
missing they typically can be calculated from the others. Using summary
statistics is also often the only possible way for conducting the replication
success analysis as the raw data from the original study may not be available to
the researchers conducting the replication study. The most important statistic
is the effect estimate $\that$. It provides an estimate of the underlying effect
size $\theta$ which quantifies the true effect or association of an
intervention/exposure with an outcome variable. Typical effect sizes are mean
differences and correlations (for continuous outcomes), odds ratios (for binary
outcomes), or hazard ratios (for time-to-event outcomes). Depending on the type
of effect size, a transformation might be required so that the assumption of
approximately normally distributed effect estimates around the unknown effect
size $\theta$ (for large enough sample sizes) is justified. This could be, for
instance, the Fisher $z$-transformation for correlations or the
log-transformation for odds/hazard ratios \citep[chapter 11]{Cooper2019}. The
associated standard error $\sigma$ represents the statistical uncertainty of the
estimate. Typically, the available standard error $\sigma$ is only an estimate
of the true standard error. However, in most parts of this thesis it will be
assumed that $\sigma$ corresponds to the true standard error. This is the same
assumption as in ordinary fixed-effect/random-effects meta-analysis, and
typically reasonable if the sample size of the studies is not too small. Under
the assumption of (asymptotic) normality, confidence intervals for $\theta$ and
$p$-values for testing the null hypothesis $H_{0} \colon \theta = 0$ can be
computed as shown in Table~\ref{tab:meta}.

@@

The remaining criteria in Table~\ref{tab:rsdef} put more emphasis on
compatibility in effect size between the original and the replication study. For
example, the relative effect estimate $d = \that_{r}/\that_{o}$ quantifies how
much the magnitude of the replication effect estimate changed compared to the
original, and the smaller $d$ is the smaller the degree of replication success.
Some projects also report a confidence interval for $d$ \citep{Camerer2016,
  Camerer2018}, whereas others ignore its uncertainty and make a binary cut at
$d_{\text{min}} = 1$ to define replication success \citep{Errington2021}. The
criteria based on confidence and prediction intervals define effect size
compatibility on an absolute scale. However, the criterion based on the original
confidence interval ignores the uncertainty from the replication, whereas the
criterion based on the replication confidence interval ignores the uncertainty
from the original study. The prediction interval criterion takes into account
both sources of uncertainty \citep{Patil2016}. Yet, declaring ``replication
success'' based on the prediction interval may be logically questionable due to
its connection to the meta-analytic $Q$-test.
% as it may also be seen as an instance of the ``absence of evidence fallacy''
% \citep{Altman1995};
That is, if the $p$-value from the $Q$-test is larger than $\alpha$ this is
equivalent to the replication effect estimate $\that_{r}$ being contained in its
$(1- \alpha)$ prediction interval. The null hypothesis of this test is defined
that the underlying effect sizes of original and replication study are the same
($H_{0} \colon \theta_{o} = \theta_{r}$), so a rejection of this null hypothesis
corresponds to demonstrating replication failure and not replication success.
Interpreting a failure to reject the null hypothesis as evidence for it is again
an instance of the ``absence of evidence fallacy''
\citep{Hedges2019}. % To establish replication success a
% test based on the null hypothesis $H_{0} \colon \theta_{o} \neq \theta_{r}$
% would be required \citep{Hedges2019}.
As in the case of defining replication success by simultaneous non-significance
of original and replication study, the mismatch of the null hypothesis of the
prediction interval criterion results in the undesirable property that
``replication success'' can almost always be achieved if the sample size of the
studies is small enough as the prediction interval becomes wider with larger
standard errors.

@@

\subsubsection{Example ``Reproducibility Project: Cancer Biology''}
I will now illustrate the assessment of replication success on data from the
``Reproducibility Project: Cancer Biology'' \citep{Errington2021}. This
large-scale project attempted to replicate 53 landmark studies from the field of
cancer biology \citep[and would perhaps therefore better be named ``Replication
Project'', see][for the distinction between ``replicabality'' and
``reproducibility'']{Goodman2016}. In the end, only 23 of the 53 studies could
be repeated due to various difficulties, such as, missing information from the
original studies or problems in conducting the experiments.
\citet{Errington2021} report that these experiments led to data on 158
quantitative effects. However, from the data which they provide only 132
quantitative effects are provided with original and replication standardized
mean difference effect estimates along with standard errors, and only they will
be used in the subsequent analyses.

@@

A detailed view for a subset of the data from the project is given in
Table~\ref{tab:RPCB}. The subset is chosen such that from every original study
one effect and one replication of that effect is included. For the three
replications at the bottom of the table (\#18, \#19, and \#20), all criteria
indicate replication failure. For the remaining majority of the studies, the
conclusions are more ambiguous; for no single replication study are all criteria
satisfied simultaneously. For instance, the first three studies satisfy the
significance criterion ($p_{o} < 0.05$ and $p_{r} < 0.05$), meta analytic
significance ($p_{m} < 0.05$) and the $Q$-test/prediction interval criterion
($p_{Q} > 0.05$), yet the replication effect estimate is smaller than the
original one ($d < 1$).
% For example, replication \#17 is a clear
% failure with respect to the relative effect estimate ($d < 1$) and the
% significance criteria ($p_{o} > 0.05$ and $p_{r} > 0.05$), yet the $Q$-test does
% not indicate evidence for inconsistency of the two effect estimates
% ($p_{Q} > 0.05$).

@@

\subsection{Reverse-Bayes assessment of replication studies}
In response to the lack of a standard criterion for replication success, various
methods have been proposed \citep[among others]{Verhagen2014, Simonsohn2015,
  Anderson2016, Patil2016, Johnson2016, Etz2016, vanAert2017, Ly2018, Harms2019,
  Hedges2019, Mathur2020, Held2020, Pawel2020, Bonett2020}. The focus of this
thesis is to refine and extend the proposal from \citet{Held2020} which combines
\emph{reverse-Bayes inference} and \emph{Bayesian model criticism} in a method
for assessing replication success. In the following, I will summarize its main
ideas and technical underpinnings.

@@

This shows that the reverse-Bayes approach based on sceptical priors can be used
to formally challenge the finding of an original study. However, once this
sceptical prior is determined, the question becomes whether it is plausible in
light of external data. A natural candidate for answering the question is data
from a replication study. In the following, I will show how Bayesian model
criticism can be used for doing so.

% \begin{figure}[!htb]
%   \centering
%   \begin{tikzpicture}[node distance = 5em, thick]
%     % nodes %
%     \node[text width=5em, text centered] (data) {Likelihood $f(\text{data} \,|\, \theta)$};
%     \node[text width=3em, text centered] (prior) [left=6.5em of data] {Prior $f(\theta)$};
%     \node[text width=5em, text centered] (post) [right=5em of data] {Posterior $f(\theta \,|\, \text{data})$};
%     \node[text width=10em, text centered] (RBinference) [below of=prior] {Reverse-Bayes inference};
%     \node[text width=10em, text centered] (FBinference) [below of=post] {Forward-Bayes inference};

%     % edges %
%     \draw [->, dotted] (prior) to [out=45, in=135, looseness=0.3] node[above]{Bayesian updating} (post);
%     \draw [->, dashed] (post) to [out=225, in=315, looseness=0.3] node[below]{Bayesian downdating} (prior);
%     \draw [->, dashed] (prior) to [out=270, in=90, looseness=0] (RBinference);
%     \draw [->, dotted] (post) to [out=270, in=90, looseness=0] (FBinference);
%   \end{tikzpicture}
%   \caption{Schematic illustration of forward-Bayes and reverse-Bayes inference
%     for an unknown parameter $\theta$.}
%   \label{fig:illustrationRB}
% \end{figure}

@@

% In general,
% a distinction can be made between checking for \emph{likelihood-data conflict}
% and checking for \emph{prior-data conflict}. In the following, we will assume
% that the likelihood is adequate and focus on the

We now return to the replication setting. Having obtained a sceptical prior
$\theta \sim \Nor(0, \tau^{2}_{\alpha})$ with sufficiently sceptical prior
variance $\tau^{2}_{\alpha}$ from~\eqref{eq:tau2alpha}, the aim is to assess its
adequacy in light of the data from a replication study. If we are able to show
that the prior is inadequate, this would demonstrate that scepticism regarding
the original finding is unjustified and that the original study provided
evidence for a genuine effect. Under the assumption of a normal likelihood for
the replication effect estimate, \ie{}
$\that_{r} \given \theta \sim \Nor(\theta, \sigma^{2}_{r})$, the prior
predictive distribution is given by
$\that_{r} \given \theta \sim \Nor(0, \sigma^{2}_{r} + \tau^{2}_{\alpha})$. As
the prior predictive distribution is symmetric around zero, the prior predictive
$p$-value~\eqref{eq:pppval} is
% the probability of observing replication effects larger in absolute value than
% the observed one $\that_{r}$ under
\begin{align}
  p_{\text{Box}}
  = 2\left\{1 - \Phi\left(\frac{|\that_{r}|}{\sqrt{\sigma^{2}_{r} +
  \tau^{2}_{\alpha}}}\right)\right\}.
  \label{eq:pboxNorm}
\end{align}

@@

There is one problem with the (two-sided) sceptical $p$-value as defined
in~\eqref{eq:ps}; It does not take the direction of the effect estimates into
account, so replication success may be established even though the effect
estimate from the replication goes in the opposite direction of the original one
($\sign(\that_{o}) \neq \sign(\that_{r})$). In fact, the sceptical $p$-value
will decrease with decreasing negative relative effect estimate
($\ps \downarrow p_{o}$ as $d \downarrow -\infty$ for fixed $\sigma_{o}$ and
$\sigma_{r}$) which seems contrary to intuitive understandings of replicability
as a change in effect direction may diminish the usefulness of a scientific
finding (\eg{} a negative treatment effect may indicate harm instead of
benefit).
% For example, if $\that_{o} = \Sexpr{smdo}$,
% $\that_{r} = \Sexpr{smdr}$, and $\sigma_{o} = \sigma_{r} = 1$, this would lead
% to $\ps = \Sexpr{pFormat(ps1)}$, and the sceptical $p$-value continues to
% decreases with decreasing replication effect estimates.
This ``replication
paradox'' \citep{Ly2018} can be avoided by defining a one-sided sceptical
$p$-value
\begin{align*}
  p_{\text{S}} =
  \begin{cases}
   1 - \Phi(|z_{\text{S}}|) & \text{if} ~\sign(\that_{o}) = \sign(\that_{r}) \\
   \Phi(|z_{\text{S}}|) & \text{if} ~ \sign(\that_{o}) \neq \sign(\that_{r}) \\
  \end{cases}
\end{align*}
similar to how ordinary one-sided $p$-values are defined. In the subsequent
chapters only the one-sided version of the sceptical $p$-value will be used.

The results from the ``Reproducibility Project: Cancer Biology'' in
Table~\ref{tab:RPCB} illustrate the properties of the sceptical $p$-value. For
example, study \#4 fails to achieve replication success at level
$\alpha = 2.5\%$ with the one-sided sceptical $p$-value, even though the
replication study was highly convincing (the effect estimate was almost five
times as large as in the original study). Yet, as the approach requires both
studies to be convincing on their own -- and the original study was not
significant at the 2.5\% level (one-sided) -- replication success at this level
is impossible with the sceptical $p$-value. The second property is illustrated
by study \#8. Here the original study was convincing and the replication study
also achieved significance. However, the effect estimate from the replication
was roughly 60\% smaller than the one from the original study, and significance
is merely achieved because the standard error was much smaller (\ie{} around
$1/\surd c \approx 1/2.8$ times smaller). The sceptical $p$-value is therefore
only $p_{\text{S}} = 0.12$, indicating hardly any evidence for replication
success.

@@

This thesis consists of six papers divided into three parts. The first part
(Paper~\ref{PaperI}, \ref{PaperII}, and \ref{PaperIII}) focuses on methodology
for design and analysis of replication studies. The second part
(Paper~\ref{PaperIV} and \ref{PaperV}) revolves around reverse-Bayes methodology
with a broader scope of applications than replication
studies. % Paper IV is a review paper about
% reverse-Bayes methodology and Paper V is a short comment on another article
% which proposed a reverse-Bayes method.
The last part (Paper~\ref{PaperVI}) deals with meta-scientific perspectives of
methodological research.
% The article lists and illustrates questionable
% research practices in simulation studies, and gives recommendations how to avoid
% them.

@@

L. Held had the idea to apply the sceptical $p$-value method to the data from
the four replication projects, which I collected for my master thesis. L. Held
and C. Micheloud came up with the golden level. L. Held wrote an initial draft
of the manuscript. L. Held, C. Micheloud, and I then iteratively worked on the
manuscript.

@@

The reverse-Bayes approach from \citet{Held2020} is based on challenging the
original study with a sceptical prior so there is no longer evidence for an
effect. Evidence is quantified in terms of credible intervals and tail
probabilities. However, there exist also other measures of evidence, and it has
been a matter of long debates which is the most appropriate \citep[see
\eg{}][]{Berger1987, Casella1987, Royall1997, Berger2003, Benjamin2017,
  Lakens2018, Amrhein2019b}. In this paper, we extend the reverse-Bayes
assessment of replication studies to use Bayes factors \citep{Good1958,
  Jeffreys1961} for quantifying evidence and prior-data
conflict. % Bayes factors are also
% used for prior-data conflict assessment as suggested by \citep{Box1980}.
Similar to the sceptical $p$-value, the procedure leads to a single measure for
quantifying the degree of replication success, \emph{the sceptical Bayes
  factor}. Systematic comparisons show that the sceptical Bayes factor has
similar properties as the sceptical $p$-value due to the reverse-Bayes approach
underlying both methods (\eg{} it penalizes shrinkage of the replication effect
estimate and requires compelling evidence from both studies in terms of
$p$-values and Bayes factors, respectively). However, it is also shown that the
sceptical $p$-value suffers from a certain type of ``shrinkage paradox'', which
is avoided by the sceptical Bayes factor; when the $p$-value from the original
study goes to zero, replication success based on the sceptical $p$-value can be
achieved with any arbitrarily small replication effect estimate, whereas
replication success based on the sceptical Bayes factor poses a finite limit on
how much shrinkage is allowed. Technically, the procedure is more involved and
closed-form solutions for the sceptical Bayes factor are only available in
special situations. % and in terms of the
% ``Lambert W function'' \citep{Corless1996}.
The method is illustrated on data from the ``Social Sciences Replication
Project'' \citep{Camerer2018}, and implemented in the R package
\texttt{BayesRep} (\url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}).

@@

An important aspect in the design of replication studies is determining their
sample size. How exactly the sample size should be determined depends on which
method is used for the analysis of the replication data. Various approaches have
been proposed for doing so which are specifically tailored to certain analysis
methods. In this article, we provide a general Bayesian framework which applies
to any analysis method (including the sceptical $p$-value and the sceptical
Bayes factor). We show how the data from the original study and external
knowledge can be combined in a \emph{design prior} for the underlying model
parameters. Based on this design prior, predictions about the replication data
can then be computed, and the replication sample size can be chosen such that
the probability of replication success becomes as high as desired. We illustrate
Bayesian design of replication studies in the normal-normal hierarchical model
which provides sufficient flexibility for specification of design priors. Data
from a cross-laboratory replication project \citep{Protzko2020} are used for
illustrating our methods, which are available in the R package
\texttt{BayesRepDesign} (\url{https://github.com/SamCH93/BayesRepDesign}).

@@

L. Held and M. Ott started working on this article several years ago. When I
discovered the connection between the Analysis of Credibility and the fail-safe
$N$ method \citep{Rosenthal1979,Rosenberg2005}, L. Held suggested that it would
fit nicely into this manuscript, to add the COVID-19 meta-analysis example, and
that I should start to overhaul it. I rewrote and expanded his initial draft,
adding also a new section on reverse-Bayes approaches with Bayes factors,
largely based on the work from Paper~\ref{PaperII}. We then managed to recruit R. Matthews
to also contribute. From that point on the three of us iteratively worked on the
manuscript and M. Ott gave high-level feedback.

@@

Shortly after the acceptance of Paper~\ref{PaperIII}, the article by
\citet{Sondhi2021} appeared. It proposed a novel reverse-Bayes method called
\emph{Bayesian Additional Evidence}, and we noted some flaws in the article.
This prompted us to write a commentary. We show that -- contrary to the
statement by Sondhi et al. -- there is a closed form solution for the key
quantity in their approach termed ``Bayesian Additional Evidence tipping
point''.
% The Bayesian Additional Evidence method provides an answer to the question
% ``What prior do I have to choose so that that my unconvincing data become
% convincing?''.
The method is also closely related to the Analysis of Credibility by
\citet{Matthews2018}. We investigate differences and similarities of the two
methods, showing that the priors determined through the Bayesian Additional
Evidence method are not always helpful.

R. Matthews alerted us about the article from \citet{Sondhi2021}. After reading
it, I realized that their statement about closed-form solutions was incorrect
and derived a solution. \mbox{L. Held} suggested to write a commentary. I wrote
an initial draft of the manuscript, which \mbox{R. Matthews} substantially
improved by expanding it with some logical flaws of the method. The two of us
iteratively worked on the manuscript, while L. Held gave high-level feedback.

>>>>

% How can we know if a finding from a scientific study is really true? For
% example, how can we know if the protective effect of a vaccine found in a study
% is real? The answer to such questions is of high importance to scientists,
% decision makers, and the general population. However, because any study result
% comes with uncertainty we can never know for sure.
How can we know whether we can trust a finding from a scientific study? For
example, how can we know whether the protective effect of a vaccine found in a
study is indeed existent or whether it is just a spurious finding? The answer to
such questions is of high importance to researchers, decision makers, and the
general population, and one way to address them scientifically is through
\emph{replication studies}.

A replication study consists of repeating the original study as closely as
possible but with new subjects. Such a study may yield similar results which
would make us more confident about the original finding, or may yield
conflicting results which would lower our confidence. As such, replication
studies are an essential part of the scientific method as they provide a means
for substantiating genuine research findings and refuting research findings
which occurred merely by chance. For this reason, ``successful'' replication is
often a requirement, for instance, for acceptance of newly proposed scientific
theories (\eg{} a new physical model) or the implementation of policies based on
scientific knowledge (\eg{} market approval of a drug). The results from
replication studies may hence have real world consequences, % , such as deciding
% whether we receive the recommendation to get vaccinated (a consequence that
% anyone who experienced the COVID-19 pandemic is very aware of)
and it is therefore important that methodological aspects of replication
studies, such as their statistical design and analysis, are well understood.

@@

Most methods for analyzing replication studies can be formulated in terms of
study-level summary statistics as shown in Table~\ref{tab:meta}. % Effect
% estimates, standard error, confidence intervals, and $p$-values
All of these are routinely reported in research articles, and if one of them is
missing they can typically be calculated from the others. Using summary
statistics is also often the only possible way for conducting the replication
success analysis as the raw data from the original study may not be available to
the researchers conducting the replication study. The most important statistic
is the effect estimate $\that$. It provides an estimate of the underlying effect
size $\theta$ which quantifies the true effect or association of an
intervention/exposure with an outcome variable. Typical effect sizes are mean
differences and correlations (for continuous outcomes), odds ratios (for binary
outcomes), or hazard ratios (for time-to-event outcomes). Depending on the type
of effect size, a transformation might be required so that the assumption of
approximately normally distributed effect estimates around the unknown effect
size $\theta$ (for large enough sample sizes) is justified. This could be, for
instance, the Fisher $z$-transformation for correlations or the
log-transformation for odds/hazard ratios \citep[chapter 11]{Cooper2019}. The
associated standard error $\sigma$ represents the statistical uncertainty of the
estimate. Typically, the available standard error $\sigma$ is only an estimate
of the true standard error. However, in most parts of this thesis it will be
assumed that $\sigma$ corresponds to the true standard error. This is the same
assumption as in ordinary fixed-effect/random-effects meta-analysis, and
typically reasonable if the sample size of the studies is not too small. Under
the assumption of (asymptotic) normality, confidence intervals for $\theta$ and
$p$-values for testing the null hypothesis $H_{0} \colon \theta = 0$ can be
computed as shown in Table~\ref{tab:meta}.

@@

The remaining criteria in Table~\ref{tab:rsdef} put more emphasis on
compatibility in effect size between the original and the replication study. For
example, the relative effect estimate $d = \that_{r}/\that_{o}$ quantifies how
much the magnitude of the replication effect estimate changed compared to the
original, and the smaller $d$ is the smaller the degree of replication success.
Some projects also report a confidence interval for $d$ \citep{Camerer2016,
  Camerer2018}, whereas others ignore its uncertainty and make a binary cut at
$d_{\text{min}} = 1$ to define replication success \citep{Errington2021}. The
criteria based on confidence and prediction intervals define effect size
compatibility on an absolute scale. However, the criterion based on the original
confidence interval ignores the uncertainty from the replication, whereas the
criterion based on the replication confidence interval ignores the uncertainty
from the original study. The prediction interval criterion takes into account
both sources of uncertainty \citep{Patil2016}. Yet, declaring ``replication
success'' based on the prediction interval may be logically questionable due to
its connection to the meta-analytic $Q$-test.
% as it may also be seen as an instance of the ``absence of evidence fallacy''
% \citep{Altman1995};
That is, if the $p$-value from the $Q$-test is larger than $\alpha$ this is
equivalent to the replication effect estimate $\that_{r}$ being contained in its
$(1- \alpha)$ prediction interval. The null hypothesis of this test is defined
that the underlying effect sizes of original and replication study are the same
($H_{0} \colon \theta_{o} = \theta_{r}$), so a rejection of this null hypothesis
corresponds to demonstrating replication failure and not replication success.
Interpreting a failure to reject the null hypothesis as evidence for it is again
an instance of the ``absence of evidence fallacy''
\citep{Hedges2019}. % To establish replication success a
% test based on the null hypothesis $H_{0} \colon \theta_{o} \neq \theta_{r}$
% would be required \citep{Hedges2019}.
As in the case of defining replication success by simultaneous non-significance
of original and replication study, the mismatch of the null hypothesis of the
prediction interval criterion results in the undesirable property that
``replication success'' can almost always be achieved if the sample size of the
studies is small enough, because the prediction interval becomes wider with
larger standard errors.

@@

\subsubsection{Example ``Reproducibility Project: Cancer Biology''}
I will now illustrate the assessment of replication success on data from the
``Reproducibility Project: Cancer Biology'' \citep{Errington2021}. This
large-scale project attempted to replicate 53 landmark studies from the field of
cancer biology \citep[and would perhaps better be named ``Replication Project'',
see][for the distinction between ``replicabality'' and
``reproducibility'']{Goodman2016}. In the end, only 23 of the 53 studies could
be repeated due to various difficulties, such as, missing information from the
original studies or problems in conducting the experiments.
\citet{Errington2021} report that these experiments led to data on 158
quantitative effects. However, from the data which they provide only 132
quantitative effects are provided with original and replication standardized
mean difference effect estimates along with standard errors, and only they will
be used in the subsequent analyses.

@@

A detailed view for a subset of the data from the project is given in
Table~\ref{tab:RPCB}. The subset is randomly chosen such that from every
original study one effect and one replication of that effect is included. For
the three replications at the bottom of the table (\#18, \#19, and \#20), all
criteria indicate replication failure. For the other replications, the
conclusions are more ambiguous as in no single case are all criteria met
simultaneously. For instance, the first three replications satisfy the
significance criterion ($p_{o} < 0.05$ and $p_{r} < 0.05$), the meta analytic
significance criterion ($p_{m} < 0.05$) and the $Q$-test/prediction interval
criterion ($p_{Q} > 0.05$), yet the replication effect estimate is smaller than
the original one so does not satisfy the relative effect size criterion
($d < 1$). The fourth replication, on the other hand, satisfies the relative
effect size criterion ($d \geq 1$) but fails to satisfy the significance
criterion as the original study was not significant ($p_{o} > 0.05$).
% For example, replication \#17 is a clear
% failure with respect to the relative effect estimate ($d < 1$) and the
% significance criteria ($p_{o} > 0.05$ and $p_{r} > 0.05$), yet the $Q$-test does
% not indicate evidence for inconsistency of the two effect estimates
% ($p_{Q} > 0.05$).

@@

\subsection{Reverse-Bayes assessment of replication studies}
In response to the lack of a standard criterion for replication success, various
methods have been proposed \citep[among others]{Verhagen2014, Simonsohn2015,
  Anderson2016, Patil2016, Johnson2016, Etz2016, vanAert2017, Ly2018, Harms2019,
  Hedges2019, Mathur2020, Held2020, Pawel2020, Bonett2020}. The focus of this
thesis is to refine and extend the proposal from \citet{Held2020} which combines
\emph{reverse-Bayes inference} and \emph{Bayesian model criticism} in a method
for assessing replication success. In the following, I will summarize the
methods and its technical underpinnings.

@@

In this way the reverse-Bayes approach based on sceptical priors can be used to
formally challenge the finding from an original study. However, once this
sceptical prior is determined, the question becomes whether it is plausible in
light of external data. A natural candidate for answering the question is data
from a replication study. In the following, I will show how Bayesian model
criticism can be used for doing so.

@@

We now return to the replication setting. Having obtained a sceptical prior
$\theta \sim \Nor(0, \tau^{2}_{\alpha})$ with sufficiently sceptical prior
variance $\tau^{2}_{\alpha}$ from~\eqref{eq:tau2alpha}, the aim is to assess its
adequacy in light of the data from a replication study. If we are able to show
that the prior is inadequate, this would demonstrate that scepticism regarding
the original finding is unjustified and that the original study provided
evidence for a genuine effect. Under the assumption of a normal likelihood for
the replication effect estimate, \ie{}
$\that_{r} \given \theta \sim \Nor(\theta, \sigma^{2}_{r})$, the prior
predictive distribution is given by
$\that_{r} \given \theta \sim \Nor(0, \sigma^{2}_{r} + \tau^{2}_{\alpha})$. As
the prior predictive distribution is symmetric around zero, the prior predictive
$p$-value~\eqref{eq:pppval} is
\begin{align}
  p_{\text{Box}}
  = 2\left\{1 - \Phi\left(\frac{|\that_{r}|}{\sqrt{\sigma^{2}_{r} +
  \tau^{2}_{\alpha}}}\right)\right\}.
  \label{eq:pboxNorm}
\end{align}

@@

There is one problem with the (two-sided) sceptical $p$-value as defined
in~\eqref{eq:ps}; It does not take the direction of the effect estimates into
account, so replication success may be established even though the effect
estimate from the replication goes in the opposite direction of the original one
($\sign(\that_{o}) \neq \sign(\that_{r})$). In fact, the sceptical $p$-value
will decrease with decreasing negative relative effect estimate
($\ps \downarrow p_{o}$ as $d \downarrow -\infty$ for fixed $\sigma_{o}$ and
$\sigma_{r}$) which seems contrary to intuitive understandings of replicability
as a change in effect direction may diminish the usefulness of a scientific
finding (\eg{} a negative treatment effect may indicate harm instead of
benefit).
% For example, if $\that_{o} = \Sexpr{smdo}$,
% $\that_{r} = \Sexpr{smdr}$, and $\sigma_{o} = \sigma_{r} = 1$, this would lead
% to $\ps = \Sexpr{pFormat(ps1)}$, and the sceptical $p$-value continues to
% decreases with decreasing replication effect estimates.
This ``replication
paradox'' \citep{Ly2018} can be avoided by defining a one-sided sceptical
$p$-value
\begin{align*}
  p_{\text{S}} =
  \begin{cases}
   1 - \Phi(|z_{\text{S}}|) & \text{if} ~\sign(\that_{o}) = \sign(\that_{r}) \\
   \Phi(|z_{\text{S}}|) & \text{if} ~ \sign(\that_{o}) \neq \sign(\that_{r}) \\
  \end{cases}
\end{align*}
similar to how ordinary one-sided $p$-values are defined. The one-sided
sceptical $p$-value has similar properties as the two-sided version -- it is
always larger than the one-sided $p$-values from original and replication
studies, and it penalizes shrinkage of the replication effect estimate. In the
subsequent chapters only the one-sided version of the sceptical $p$-value will
be used.

The last column of Table~\ref{tab:RPCB} shows the one-sided sceptical $p$-value
for the subset of replications from the ``Reproducibility Project: Cancer
Biology''. The results illustrate the previously discussed properties to require
significance from both studies and to penalize effect shrinkage. For example,
replication \#4 fails to achieve replication success at level $\alpha = 2.5\%$
with the one-sided sceptical $p$-value, even though the replication study was
highly convincing (the effect estimate was almost five times as large as in the
original study). Yet, as the approach requires both studies to be convincing on
their own -- and the original study was not significant at the 2.5\% level
(one-sided) -- replication success at this level is impossible with the
sceptical $p$-value. The second property is illustrated by replication \#8. Here
both the original and replication studies were significance. However, the effect
estimate from the replication was roughly 60\% smaller than the one from the
original study, and significance is merely achieved because the standard error
was much smaller (\ie{} around $1/\surd c \approx 1/2.8$ times smaller). The
sceptical $p$-value is therefore only $p_{\text{S}} = 0.12$, indicating less
evidence for replication success.

@@

This thesis consists of six papers divided into three parts. The first part
(Paper~\ref{PaperI}, \ref{PaperII}, and \ref{PaperIII}) focuses on methodology
for design and analysis of replication studies. The second part
(Paper~\ref{PaperIV} and \ref{PaperV}) revolves around reverse-Bayes methodology
with a broader scope of applications than replication
studies. % Paper IV is a review paper about
% reverse-Bayes methodology and Paper V is a short comment on another article
% which proposed a reverse-Bayes method.
The last part (Paper~\ref{PaperVI}) deals with integrity issues in
methodological research.
% The article lists and illustrates questionable
% research practices in simulation studies, and gives recommendations how to avoid
% them.

@@

L. Held had the idea to apply the sceptical $p$-value to the data from the four
replication projects, which I collected for my master thesis. L. Held and C.
Micheloud came up with the golden level. L. Held wrote an initial draft of the
manuscript. L. Held, C. Micheloud, and I then iteratively worked on the
manuscript.

@@

The reverse-Bayes approach from \citet{Held2020} is based on challenging the
original study with a sceptical prior so there is no longer evidence for an
effect. Evidence is quantified in terms of credible intervals and tail
probabilities. However, there exist also other measures of evidence, and it has
been a matter of long debates which is the most appropriate \citep[see
\eg{}][]{Berger1987, Casella1987, Royall1997, Berger2003, Benjamin2017,
  Lakens2018, Amrhein2019b}. In this paper, we extend the reverse-Bayes
assessment of replication studies to use Bayes factors \citep{Good1958,
  Jeffreys1961} for quantifying evidence and prior-data
conflict. % Bayes factors are also
% used for prior-data conflict assessment as suggested by \citep{Box1980}.
Similar to the sceptical $p$-value, the procedure leads to a single measure for
quantifying replication success, \emph{the sceptical Bayes factor}. Systematic
comparisons show that the sceptical Bayes factor has similar properties as the
sceptical $p$-value %due to the reverse-Bayes approach underlying both methods
(\eg{} it penalizes shrinkage of the replication effect estimate and requires
compelling evidence from both studies in terms of $p$-values and Bayes factors,
respectively). However, it is also shown that the sceptical $p$-value suffers
from a certain type of ``shrinkage paradox'', which is avoided by the sceptical
Bayes factor; when the $p$-value from the original study goes to zero,
replication success based on the sceptical $p$-value can be achieved with any
arbitrarily small replication effect estimate, whereas replication success based
on the sceptical Bayes factor poses a finite limit on how much shrinkage is
allowed. Technically, the procedure is more involved and closed-form solutions
for the sceptical Bayes factor are only available in special
situations. % and in terms of the
% ``Lambert W function'' \citep{Corless1996}.
The method is illustrated on data from the ``Social Sciences Replication
Project'' \citep{Camerer2018}, and implemented in the R package
\texttt{BayesRep} (\url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}).

@@

An important aspect in the design of replication studies is determining their
sample size. How exactly the sample size should be determined depends on which
method is used for the analysis of the replication data. Various approaches have
been proposed for doing so which are specifically tailored to certain analysis
methods. In this article, we provide a general Bayesian framework which applies
to any analysis method (including the sceptical $p$-value and the sceptical
Bayes factor). We show how the data from the original study and external
knowledge can be combined in a \emph{design prior} for the underlying model
parameters. Based on this design prior, predictions about the replication data
can be computed, and the replication sample size can be chosen such that the
probability of replication success becomes as high as desired. We illustrate
Bayesian design of replication studies in the normal-normal hierarchical model
which provides sufficient flexibility for specification of design priors. Data
from a cross-laboratory replication project \citep{Protzko2020} are used for
illustrating our methods, which are available in the R package
\texttt{BayesRepDesign} (\url{https://github.com/SamCH93/BayesRepDesign}).

@@

L. Held and M. Ott started working on this article several years ago. When I
discovered the connection between the Analysis of Credibility and the fail-safe
$N$ method \citep{Rosenthal1979,Rosenberg2005}, L. Held suggested that it would
fit nicely into this manuscript and to add the COVID-19 meta-analysis example. I
rewrote and expanded his initial draft, adding also a new section on
reverse-Bayes approaches with Bayes factors, largely based on the work from
Paper~\ref{PaperII}. We then managed to recruit R. Matthews to also contribute.
From that point on the three of us iteratively worked on the manuscript and M.
Ott gave high-level feedback.

@@

Shortly after the acceptance of Paper~\ref{PaperIV}, the article by
\citet{Sondhi2021} appeared. It proposed a novel reverse-Bayes method called
\emph{Bayesian Additional Evidence}, and we noted some flaws in the article.
This prompted us to write a commentary. We show that -- contrary to the
statement by Sondhi et al. -- there is a closed form solution for the key
quantity in their approach termed ``Bayesian Additional Evidence tipping
point''.
% The Bayesian Additional Evidence method provides an answer to the question
% ``What prior do I have to choose so that that my unconvincing data become
% convincing?''.
The method is also closely related to the Analysis of Credibility by
\citet{Matthews2018}. We investigate differences and similarities of the two
methods, concluding that the priors determined through the Bayesian Additional
Evidence method are of limited use due to their restrictive assumption of having
equal variance as the data.

R. Matthews alerted us about the article from \citet{Sondhi2021}. After reading
it, I realized that their statement about closed-form solutions was incorrect
and derived a solution. \mbox{L. Held} suggested to write a commentary. I wrote
an initial draft of the manuscript, which \mbox{R. Matthews} improved by
discussing some logical flaws of the method. The two of us iteratively worked on
the manuscript, while L. Held gave high-level feedback.
